Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex

\section{Approach}
\label{sec:approach}

@@

To illustrate the idea behind the \sfl{}+\cs{} combination, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).

>>>>

\section{The \comb{} Approach}
\label{sec:approach}

@@

To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).
